\documentclass[margin,line]{res}
\usepackage{pifont}
\usepackage{marvosym}



\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\textheight=11.0in %decrease bottom margin size
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}


\name{Wee Don Teo --- Resume\vspace*{.1in}} %\hfill \vspace{-0.15in} \Letter \hspace{1 mm} don.teo@gmail.com

%\hfill { }

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{3.8in}}
%{\bf Current Address}          & \hfill {\bf Permanent Address}\\
%210 Summerhill Dr., Apt. 1     & \hfill 33 Terraview Blvd.\\
%Ithaca, NY 14850 USA           & \hfill Toronto, ON, M1R 4L8, Canada \\
%\Mobilefone \hspace{1 mm} 607-220-4408           & \hfill \Telefon \hspace{1 mm} 416-383-1568 \\
%                               & \hfill {\bf After March 8}\\
%%%
%324 Physical Sciences Building & \hfill \Telefon \hspace{1 mm} 607-255-0833 \\
%Department of Physics          & \hfill \Mobilefone \hspace{1 mm} 607-220-4408 \\
%Cornell University             & \hfill \Letter \hspace{1 mm}  wt88@cornell.edu\\       
%Ithaca, NY 14853 USA           & \hfill www.lepp.cornell.edu/{\raise.17ex\hbox{$\scriptstyle\sim$}}wt88 \\     
%%%
33 Terraview Blvd.             & \hfill \Telefon \hspace{1 mm} 416-383-1568 \\
Toronto, ON                    & \hfill \Mobilefone \hspace{1 mm} 416-887-6881 \\
M1R 4L8, Canada                %& \hfill \Letter \hspace{1 mm}  wt88@cornell.edu\\       
& \hfill \Letter \hspace{1 mm}  don.teo@gmail.com\\       
%%%
\end{tabular}

%add objective for the financial positions
%\section{\sc Profile} 
%Skilled recent doctoral graduate in Physics and 5+ years of academic
%experience in quantitative research, large-scale data analysis,
%software development, and scientific instrumentation.


%\section{\sc Objective} 
%To secure a position applying 5+ years of quantitative research,
%analysis, and software skills to solve challenging data-driven
%financial and business problems.
\section{\sc Objective} 
To secure a position applying 5+ years of quantitative research,
analysis, and programming skills to solve challenging data-driven
problems.
%business problems.% in the energy sector.

%\section{\sc Research Interests}
%Bayesian statistics, spatial statistics, nonparametric regression,
%statistical methods for large datasets, statistics for public policy

\section{\sc Education}
{\bf Ph.D. Physics}, \textit{Cornell University} \hfill {\bf January,
  2013}\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
%\item[] Field: Experimental Particle Physics
\item[] Thesis: \textit{Search for Supersymmetry with b-quark Jets and Missing
\newline \hspace*{10.5 mm} Transverse Energy in pp Collisions at $\sqrt{s}=7$ TeV}
%\vspace*{.05in}
\end{list1}
%\vspace{-.05mm}
\vspace{-.1in}
{\bf M.Sc. Physics}, \textit{Cornell University} \hfill {\bf June, 2010}\\
%\vspace{-.1in}
{\bf B.Sc. Mathematics and Physics}, \textit{University of Toronto} \hfill {\bf June, 2007}\\
\vspace*{-.1in}
%\begin{list1}
%\item[] Graduated with High Distinction
%\end{list1}
%{\em Department of Mathematics and Statistics} 
%\vspace*{-.1in}
%\begin{list1}
%\item[] B.Sc. Honours, Mathematics and Physics, 2002-2007
%\end{list1}
\vspace{-.3cm}

\section{\sc Awards} 
%\vspace*{-2mm}
%\renewcommand{\arraystretch}{2}\addtolength{\tabcolsep}{-1pt}
\renewcommand{\arraystretch}{1.5}\addtolength{\tabcolsep}{-1pt}

Natural Sciences and Engineering Research Council of Canada Postgraduate Fellowship 
$\bullet$ American Association of Physics Teachers Outstanding Teaching Assistant of the Year  
$\bullet$ Dean's List
$\bullet$ Samuel Beatty In-Course Scholarship 
$\bullet$ Donald G. Ivey Scholarship in Physics


\section{\sc Work \,\,\,Experience}
%{\bf CMS Experiment}
{\bf Graduate Researcher,}
{\em Cornell University} \hfill {\bf 2008 - 2013}\\
\vspace*{-2mm}
\begin{list2}
\item Member of the Compact Muon Solenoid experiment at the Large
  Hadron Collider of the CERN laboratory in Geneva, Switzerland.
\item Worked in tight-knit teams on large-scale data analysis projects
  that successfully measured the production rate of rare particles and
  that searched for as-yet-undiscovered particles.
\item Analysis responsibilities included the processing of datasets,
  the planning and optimization of the analysis strategy, the
  determination of selection efficiencies/systematic uncertainties,
  and the development of novel background-estimation methods.
%\item Analysis results provided significant and competitive measurements
%  to the understanding of fundamental physics interactions.
%\item Analysis required significant use of Monte Carlo methods and
%  maximum likelihood fitting techniques.
\item Developed a suite of data quality monitoring visualization
  software tools that provided real-time diagnostics on the performance
  of the detector trigger systems.
\end{list2}


{\bf Graduate Teaching Assistant,}
{\em Cornell University} \hfill {\bf 2007 - 2009}\\
\vspace*{-2mm}
\begin{list2}
\item Conducted weekly tutorial and laboratory sessions, prepared
  quizzes, and graded homework sets and examinations in fundamental
  physics courses for engineers and pre-med majors.  Taught and
  supervised a total of roughly 60 students per semester.
\end{list2}

{\bf Undergraduate Research Assistant,}
{\em York University/University of Toronto} \hfill {\bf 2006 - 2007}\\
\vspace*{-2mm}
\begin{list2}
\item Implemented pattern-finding and distortion correction methods in
  C++ for calibrating beam images using a proton beam monitor system
  prototype and custom-made Monte Carlo simulations.
\item Built a complete simulation model of the beam monitor system
  using proprietary ray-tracing software for studying the effects of
  system misalignment and beam size uncertainty on the final physics
  measurement.
\end{list2}


\section{\sc Computer Skills} 
\begin{list2}
\item{\bf Analysis Tools}: Significant experience with ROOT analysis
  framework. Working knowledge of R, Excel.  Past experience in Maple,
  Mathematica.
%Experience with  financial data analysis in R, Excel.
%Microsoft Office. Experience with financial data
%  analysis techniques with R, Excel.
%  with SAS; extensive use of C and Fortran statistical libraries.
\item {\bf Languages}: Proficient in C++.  Working knowledge of Java,
  Python, SQL.  Past experience in Perl, Unix shell scripts.
  Experience with CVS, SVN revision control systems.
\item {\bf Operating Systems}:  Extensive experience with Unix/Linux, Windows. 
\end{list2}



\section{\sc Selected Publications}
\begin{list2}
%\item \textit{Search for supersymmetry in events with b-quark jets and
%  missing transverse energy in pp collisions at 7 TeV,} CMS
%  Collaboration, 2012, Submitted to PRD
\item \textit{Search for Supersymmetry in Events with b-quark Jets and Missing Transverse Energy in pp Collisions at 7 TeV,} CMS Collaboration, 2012, Phys. Rev. D 86 072010
\item \textit{Measurement of the $t\bar{t}$ Production Cross Section
  in $pp$ Collisions at 7 TeV in Lepton + Jets Events Using b-quark
  Jet Identification,} CMS Collaboration, 2011, Phys. Rev. D 84 092004
%\item \textit{CMS Data Processing Workflows during an Extended Cosmic Ray Run,} CMS Collaboration, 2010, JINST 5 T03006
\item \textit{Commissioning of the CMS High-Level Trigger with cosmic rays,} CMS Collaboration, 2010, JINST 5 T03005
\end{list2}


\section{\sc Languages}
\begin{list2}
\item Fluent: English, Mandarin. Intermediate: Cantonese, French.  Basic: Japanese.
\end{list2}


%Complete \textit{C.V.} and references available upon request.

\end{resume}
\end{document}




